\documentclass[9pt,a4paper,sans]{article}

% Packages for layout and styling
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}

% Color definitions
\definecolor{primary}{HTML}{2E2E2E}
\definecolor{linkcolor}{HTML}{0000EE}

\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=linkcolor,
    pdftitle={Saifullah Sadi - CV},
}

% Section styling
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{11pt}{5pt}

% Custom list styling
\setlist[itemize]{leftmargin=0.25in, nosep, topsep=1pt}

\begin{document}

% Header
\begin{center}
    {\huge \textbf{SAIFULLAH SADI}} \\
    \vspace{4pt}
    Senior Software Engineer | Unity Multiplayer \& Geospatial Specialist \\
    \vspace{4pt}
    Lahore, Pakistan | +92-336-6633644 | \href{mailto:saifullahsadi@hotmail.com}{saifullahsadi@hotmail.com} \\
    \href{https://linkedin.com/in/xaifullahxady}{linkedin.com/in/xaifullahxady} | \href{https://github.com/Xaifullah/Intro}{github.com/Xaifullah/Intro}
\end{center}

% Summary
\section{Professional Summary}
Senior Software Engineer with over 10 years of experience in real-time 3D, game development, and complex mapping systems. Expert in \textbf{Unreal Engine} and \textbf{Unity} for high-performance simulation and multiplayer experiences. Specialist in geospatial visualization using \textbf{Cesium.js} and \textbf{OpenLayers}. Proven track record of leading teams and managing rapid-action prototyping environments to deliver highly engaged user experiences.

% Technical Skills
\section{Technical Skills}
\begin{itemize}
    \item \textbf{Engines \& Languages:} Unreal Engine, Unity3D, C\#, C++, JavaScript, TypeScript, Node.js.
    \item \textbf{Geospatial:} Cesium.js, OpenLayers, 3D Tiles, GIS, Terrain Generation, Real-Time Maps.
    \item \textbf{AI-Driven Web \& Frontend:} Vue.js, React.js, WebGL, REST APIs.
    \item \textbf{Specialized:} Multiplayer \& Networking, Web3/Blockchain, Rendering Optimization, Physics \& Math.
    \item \textbf{Tools:} AWS, Docker, Git, CI/CD, Google Play, App Store, Steam.
\end{itemize}

% Experience
\section{Professional Experience}

\textbf{Big Immersive Pvt Ltd} \hfill \textbf{Dec 2022 -- Feb 2026 (3.2Y)} \\
\textit{Sr. Software Engineer} \hfill Lahore, Pakistan
\begin{itemize}[leftmargin=*, noitemsep, topsep=0pt]
    \item \textbf{AI-Driven Full-Stack:} Developed modular MERN/PERN applications and CI/CD pipelines using \textbf{Claude, React/Vue, Node.js, and PostgreSQL}.
    \item \textbf{Geospatial Engineering:} Built high-performance solutions using \textbf{Cesium.js} with integrated visualizations in \textbf{Vue.js and React}.
    \item \textbf{Engine Development:} Implemented advanced geospatial calculations and real-time system integrations in \textbf{Unreal Engine} and \textbf{Unity}.
    \item \textbf{Immersive Tech:} Engineered \textbf{multiplayer experiences}, custom developer tools, and \textbf{Web3.0} integrations.
    \item \textbf{System Architecture:} Designed reusable \textbf{RESTful inventory systems} and managed complex, large-scale UI user flows.
    \item \textbf{Optimization:} Delivered a \textbf{60 FPS multiplayer sandbox} featuring custom teleportation and interactive 2D-to-3D map mechanics.
    \item \textbf{Product Leadership:} Led a \textbf{3D Avatar Generator (WebGL)} from POC to production, overseeing data modeling, SDK development, and cross-platform distribution.
\end{itemize}

\vspace{8pt}

\textbf{Tribech Solution Pvt Ltd} \hfill \textbf{Oct 2020 -- Dec 2022 (2.1Y)} \\
\textit{Team Lead} \hfill Lahore, Pakistan
\begin{itemize}
    \item Managed hyper-casual genre prototyping from concept to final product in a rapid-action environment.
    \item Collaborated with art and design teams to create highly engaged user experiences.
    \item Published titles and analyses the D1 to D7 analytics \& improved to meet KPIs.
\end{itemize}

\vspace{8pt}

\textbf{MITByte} \hfill \textbf{March 2018 -- Aug 2019 (1.5Y)} \\
\textit{Project Manager \& Tech Lead} \hfill Lahore, Pakistan
\begin{itemize}
    \item Led technical development and project management for simulation, action, shooting game portfolios.
    \item Oversaw rapid prototyping cycles and cross-functional team collaboration.
\end{itemize}

\vspace{8pt}

\textbf{Galassia Studios} \hfill \textbf{Sep 2016 -- Oct 2017 (1Y)} \\
\textit{Team Lead} \hfill Lahore, Pakistan
\begin{itemize}
    \item Directed development teams in the creation and optimization of mobile game titles.
    \item Optimized draw call by 40\% using optimizations tactics.
    \item Analysed dashboards and improved gameplay user sessions. Enhanced user acquisition.
\end{itemize}

\vspace{8pt}

\textbf{Sunstar Technologies} \hfill \textbf{Sep 2015 -- Aug 2016 (1Y)} \\
\textit{Sr. Unity3D Game Developer} \hfill Lahore, Pakistan
\begin{itemize}
    \item Developed gameplay mechanics and systems for action shooting titles using Unity3D.
    \item Published titles with millions of downloads and maximise revenue.
\end{itemize}

\vspace{8pt}

\textbf{Absomech} \hfill \textbf{March 2014 -- Aug 2015 (1.5Y)} \\
\textit{Unity3D Game Developer} \hfill Lahore, Pakistan
\begin{itemize}
    \item Engineered core gameplay loops and mobile optimizations for various game genres.
\end{itemize}

% Projects
\section{Key Projects}
\begin{itemize}
    \item \textbf{Geospatial Defense Simulation:} Developed 3D strategic defense simulations in Cesium.js, integrating dynamic weather systems and complex spatial analysis tools including Line of Sight (LOS) and 3D Viewshed Analysis.
    \item \textbf{Unity Terrain Generator:} Plugin for generating real-world terrain meshes/Unity terrains from elevation data.
    \item \textbf{Cardano Island 3D (Multiplayer Metaverse):} Real-world 3D metaverse experience in Unity for the Cardano community featuring land ownership and deeds.
    \item \textbf{Maians (Avatar Creator Tool):} A 3D avatar platform integrating AI, Social Identity, and Web3.
    \item \textbf{Crib \& Condo / Gamer's Lounge:} Multiplayer virtual 3D spaces for the Virtua Metaverse allowing for personalization and social interaction.

\end{itemize}
% Personal Projects
\section{Personal Projects}
\begin{itemize}
    \item \textbf{Community App:} AI-Driven Cross-platform Flutter application featuring real-time location tracking and movement handling. Built with a Node.js/Express backend and WebSocket for live data synchronization. 
    \\ \textit{Tech: Flutter, Dart, AWS S3, PostgreSQL, Node.js, WebSockets}

    \item \textbf{Agentic AI Data Engineering Tool:} AI-Driven Web-based data science platform for automated CSV analysis and visualization. Integrated Agentic AI to recommend data-cleaning workflows and prepare datasets for Machine Learning models.
    \\ \textit{Tech: React, Python, Node.js, MongoDB, OpenAI/Gemini API}
\end{itemize}
% Education
\section{Education \& Certifications}
\begin{itemize}
    \item \textbf{Bachelor of Science in Information Technology} \hfill 2010 -- 2014 \\
    The Islamia University Of Bahawalpur, Bahawalpur, Pakistan
    \item \textbf{Google AI Essentials} \hfill Nov 2024 \\
    Coursera | Score: 80\%+ (\href{https://www.credly.com/go/5SB7Z39c}{Credly})
\end{itemize}

% Additional
\section{Additional Information}
\begin{itemize}
    \item \textbf{Languages:} Urdu (Native), English (Professional).
    \item \textbf{Interests:} Adventure motorcycle touring
    \item \textbf{Current Focus:} MCP (Model Context Protocol) and AI Agentic Systems.
\end{itemize}

\end{document}